---
title: "Introduction to the `glebe.datasets` R package"
author: "Joel D. Barnes, M.Sc. and Michelle D. Guerrero, Ph.D."
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Introduction to the `glebe.datasets` R package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
  img { border: 0;}
  p { margin-top: 1rem;line-height: 1.5rem; }
  a, a:visited { color: #00a79d; }
  a:hover { color: #333376; }
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r klippy, echo = FALSE, include = TRUE}
klippy::klippy(position = c("top", "right"))
```

## Introduction

This package contains tools to create demo datasets for instructional use (e.g., in undergraduate statistics classes).

## Installation
### Source package

Users can download and install the source package by calling the `install.packages()` function from the `utils` R package, which comes pre-installed with R.

```{r warning = FALSE, message = FALSE, eval = FALSE}
utils::install.packages(
  pkgs = "https://github.com/barnzilla/r-package-sources/raw/master/glebe.datasets_0.4.tar.gz",
  repos = NULL, 
  type = "source"
)
library(glebe.datasets)
```

### GitHub

The most recent version of the `glebe.datasets` R package is also available on GitHub: <a href="https://github.com/barnzilla/glebe.datasets" target="_blank">www.github.com/barnzilla/glebe.datasets</a>. The `devtools` R package allows users to download and install the `glebe.datasets` R package directly from GitHub.

```{r warning = FALSE, message = FALSE, eval = FALSE}
devtools::install_github("barnzilla/glebe.datasets", upgrade = "never", build_vignettes = TRUE, force = TRUE)
library(glebe.datasets)
```

```{r warning = FALSE, message = FALSE, echo = FALSE}
library(glebe.datasets)
```

Once the `glebe.datasets` R package is loaded, any available tutorials for the package, such as this vignette, can be accessed by calling the `browseVignettes()` function.

```{r warning = FALSE, message = FALSE, eval = FALSE}
browseVignettes("glebe.datasets")
```

## Getting started
### Create a demo dataset

Users can createa a demo dataset by calling the `get_dataset()` function. This function takes one argument, `n`, which represents the number of participants (rows) that will be in the dataset.

```{r}
demo_dataset <- get_dataset(n = 500)
```

### Examine the structure of the dataset

The structure of the dataset can be examined by calling the `str()` function that comes pre-installed with R.

```{r}
str(demo_dataset)
```

### Export the dataset

Users can export a demo dataset to either Excel or SPSS using the `export_dataset()` function.

```{r eval = FALSE}
export_dataset(
  demo_dataset, 
  path = "c:/users/joel/desktop/demo_dataset.xlsx", 
  type = "spss"
)

export_dataset(
  demo_dataset, 
  path = "c:/users/joel/desktop/demo_dataset.spss", 
  type = "spss"
)
```